---
title: "Análisis 5: pEhExvsUmasM"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: show

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
setwd("~/Documents/GitHub/Resultados/docs/PrimeroDiffExpAllResults/Clasificando/Abundances")
load('CheackPointOne.RData')
```

# Quinta Clasificacion: pEhExvsUmasM

```{r}
head(pEhExvsUmasM,10);
```


```{r}
nbreaks <- 10
data5 <- pEhExvsUmasM;       head(data5)
```

## Log-Normalización

```{r}
sample1   <- data5$pEhEx_1; sample2   <- data5$pEhEx_2; sample3   <- data5$pEhEx_3;
samplevs1 <- data5$UmasM_1;  samplevs2 <- data5$UmasM_2;  samplevs3 <- data5$UmasM_3;
log2sample1 <- log2(sample1+1);         log2sample2 <- log2(sample2+1)
log2sample3 <- log2(sample3+1);         log2samplevsumasM1 <- log2(samplevs1+1)
log2samplevsumasM2 <- log2(samplevs2+1); log2samplevsumasM3 <- log2(samplevs3+1)
data5 <- cbind(data5, log2sample1,log2sample2,log2sample3,
               log2samplevsumasM1,log2samplevsumasM2,log2samplevsumasM3)
head(data5)
```


```{r}
save.image('CheckPointFifth.RData')
setwd("~/Documents/GitHub/Resultados/docs/PrimeroDiffExpAllResults/Clasificando/Abundances")
#load('CheckPointTwo.RData')
```

```{r}
library(ggplot2);library(dplyr);library("fitdistrplus");
library("MASS");library("survival")
```


```{r}
head(data5)
```

## Muestra 1

```{r}
log2sample1 <- data5$log2sample1; head(mean(log2sample1)); head(sd(log2sample1))
head(log2sample1,5)
summary(data5)
ndata5    <- length(log2sample1)
hist(log2sample1, breaks = nbreaks, col= rainbow(25,0.3), 
     main = 'Log2 sample1')
```


```{r}
meanlog2sample1 <- mean(log2sample1); head(meanlog2sample1)
StdDevlog2sample1 <- sd(log2sample1); head(StdDevlog2sample1)
Normlog2sample1 <- (log2sample1-meanlog2sample1)/StdDevlog2sample1; head(Normlog2sample1)

tst<- Normlog2sample1

hist(tst, breaks = nbreaks, col= 1:5, 
     main = 'Normalized Log2sample1',
     xlab='pEhEx1',
     ylab= 'Frequency pEhEx')
```


```{r}
fw1<-fitdist(tst, "norm")
plotdist(tst, histo = TRUE, demp = TRUE)
```


```{r}
nnorm.f <- fitdist(tst,"norm")
summary(nnorm.f)
par(mfrow=c(2,2))
denscomp(nnorm.f,legendtext = 'Dist Normal')
qqcomp(nnorm.f,legendtext = 'Dist Normal')
cdfcomp(nnorm.f,legendtext = 'Dist Normal')
ppcomp(nnorm.f,legendtext = 'Dist Normal')
```


```{r}
probs <- c();
probs[8] = 0.175;  probs[9] = 0.825; 
probs[7] = 0.15;   probs[10] = 0.85;   
probs[6] = 0.125;  probs[11] = 0.875; 
probs[5] = 0.1;    probs[12] = 0.9;    
probs[4] = 0.075;  probs[13] = 0.925; 
probs[3] = 0.05;   probs[14] = 0.95;   
probs[2] = 0.025;  probs[15] = 0.975; 
probs[1] = 0.005;  probs[16] = 0.995;  
CuantilesData <- quantile(tst,prob = probs)
CuantilesModel <- qnorm(probs, mean=0, sd=1)
Cuantilillos <- t(CuantilesModel)
colnames(Cuantilillos) <- c('0.5%','2.5%','5%','7.5%',
                            '10%','12.5%','15%','17.5%',
                            '82.5%','85%','87.5%','90%',
                            '92.5%','95%','97.5%','99.5%')
Cuantilillos <- t(Cuantilillos)
colnames(Cuantilillos) <- c('Cuantiles Ajuste')
print(Cuantilillos)
```

**Cálculo de cuantiles**

```{r}
CuantilesA <- matrix(0,8,2)
CuantilesD <- matrix(0,8,2)
colnames(CuantilesA) <- c('LimInf','LimSup')
colnames(CuantilesD) <- c('LimInf','LimSup')
rownames(CuantilesA) <- c('65','70','75','80','85','90','95','99')
rownames(CuantilesD) <- c('65','70','75','80','85','90','95','99')
CuantilesA[1,1] <-CuantilesData[8]; CuantilesA[1,2] <-CuantilesData[9]
CuantilesA[2,1] <-CuantilesData[7]; CuantilesA[2,2] <-CuantilesData[10]
CuantilesA[3,1] <-CuantilesData[6]; CuantilesA[3,2] <-CuantilesData[11]
CuantilesA[4,1] <-CuantilesData[5]; CuantilesA[4,2] <-CuantilesData[12]
CuantilesA[5,1] <-CuantilesData[4]; CuantilesA[5,2] <-CuantilesData[13]
CuantilesA[6,1] <-CuantilesData[3]; CuantilesA[6,2] <-CuantilesData[14]
CuantilesA[7,1] <-CuantilesData[2]; CuantilesA[7,2] <-CuantilesData[15]
CuantilesA[8,1] <-CuantilesData[1]; CuantilesA[8,2] <-CuantilesData[16]
CuantilesD[1,1] <-Cuantilillos[8];  CuantilesD[1,2] <-Cuantilillos[9]
CuantilesD[2,1] <-Cuantilillos[7];  CuantilesD[2,2] <-Cuantilillos[10]
CuantilesD[3,1] <-Cuantilillos[6];  CuantilesD[3,2] <-Cuantilillos[11]
CuantilesD[4,1] <-Cuantilillos[5];  CuantilesD[4,2] <-Cuantilillos[12]
CuantilesD[5,1] <-Cuantilillos[4];  CuantilesD[5,2] <-Cuantilillos[13]
CuantilesD[6,1] <-Cuantilillos[3];  CuantilesD[6,2] <-Cuantilillos[14]
CuantilesD[7,1] <-Cuantilillos[2];  CuantilesD[7,2] <-Cuantilillos[15]
CuantilesD[8,1] <-Cuantilillos[1];  CuantilesD[8,2] <-Cuantilillos[16]
```

```{r}
print(CuantilesD)
```

```{r}
print(CuantilesA)
```

```{r}
col_sequence <- rainbow(n = 7, alpha = 0.35, start = 0, end = 1)
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2 pEhEx - DATA', lty = 9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[2,1], lty=2, col="darkblue"); # 70% INFERIOR
abline(v=CuantilesA[2,2], lty=2, col="darkblue") # 70% SUPERIOR
abline(v=CuantilesA[3,1], lty=2, col="aquamarine4"); # 75% INFERIOR
abline(v=CuantilesA[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesA[5,1], lty=2, col="brown"); # 85% INFERIOR
abline(v=CuantilesA[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesA[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesA[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesA[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesA[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesA[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesA[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2   pEhEx - ADJUSTED', lty=9)
abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[2,1], lty=2, col="darkblue");  # 70% INFERIOR
abline(v=CuantilesD[2,2], lty=2, col="darkblue"); # 70% SUPERIOR
abline(v=CuantilesD[3,1], lty=2, col="aquamarine4");  # 75% INFERIOR
abline(v=CuantilesD[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesD[5,1], lty=2, col="brown");  # 85% INFERIOR
abline(v=CuantilesD[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesD[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesD[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesD[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesD[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesD[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesD[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
```

### Grafica Cuantiles del $65\%$ y $80\%$

```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2  pEhEx - DATA', lty=9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2  BaseMean - ADJUSTED', lty=9)

abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
```


### Grafica Cuantiles del $70\%$ y $85\%$

```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence, 
     main = 'Normalized Log2 pEhEx - DATA', lty=9)

abline(v=CuantilesA[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesA[2,2], lty=2, col="darkblue")
abline(v=CuantilesA[5,1], lty=2, col="brown"); 
abline(v=CuantilesA[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2  pEhEx - ADJUSTED', lty=9)

abline(v=CuantilesD[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesD[2,2], lty=2, col="darkblue")
abline(v=CuantilesD[5,1], lty=2, col="brown"); 
abline(v=CuantilesD[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))

```

## Muestra 2

```{r}
log2sample2 <- data5$log2sample2; head(mean(log2sample2)); head(sd(log2sample2))
```

```{r}
head(log2sample2,5)
```

```{r}
ndata5    <- length(log2sample2)
hist(log2sample2, breaks = nbreaks, col= rainbow(25,0.3), 
     main = 'Log2 sample2')
```

**Log-normalizacion**

```{r}
meanlog2sample2 <- mean(log2sample2); head(meanlog2sample2)
StdDevlog2sample2 <- sd(log2sample2); head(StdDevlog2sample2)
Normlog2sample2 <- (log2sample2-meanlog2sample2)/StdDevlog2sample2; head(Normlog2sample2)
tst<- Normlog2sample2
```

```{r}
hist(tst, breaks = nbreaks, col= 1:5, 
     main = 'Normalized Log2sample1',
     xlab='pEhEx1',
     ylab= 'Frequency pEhEx')
```

**Ajuste de modelo**

```{r}
fw1<-fitdist(tst, "norm")
plotdist(tst, histo = TRUE, demp = TRUE)
```



```{r}
nnorm.f <- fitdist(tst,"norm")
summary(nnorm.f)
par(mfrow=c(2,2))
denscomp(nnorm.f,legendtext = 'Dist Normal')
qqcomp(nnorm.f,legendtext = 'Dist Normal')
cdfcomp(nnorm.f,legendtext = 'Dist Normal')
ppcomp(nnorm.f,legendtext = 'Dist Normal')
```

```{r}
probs <- c();
probs[8] = 0.175;  probs[9] = 0.825; 
probs[7] = 0.15;   probs[10] = 0.85;   
probs[6] = 0.125;  probs[11] = 0.875; 
probs[5] = 0.1;    probs[12] = 0.9;    
probs[4] = 0.075;  probs[13] = 0.925; 
probs[3] = 0.05;   probs[14] = 0.95;   
probs[2] = 0.025;  probs[15] = 0.975; 
probs[1] = 0.005;  probs[16] = 0.995;  
```

```{r}
CuantilesData <- quantile(tst,prob = probs)
CuantilesModel <- qnorm(probs, mean=0, sd=1)
Cuantilillos <- t(CuantilesModel)
colnames(Cuantilillos) <- c('0.5%','2.5%','5%','7.5%',
                            '10%','12.5%','15%','17.5%',
                            '82.5%','85%','87.5%','90%',
                            '92.5%','95%','97.5%','99.5%')
Cuantilillos <- t(Cuantilillos)
colnames(Cuantilillos) <- c('Cuantiles Ajuste')
print(Cuantilillos)
```

```{r}
CuantilesA <- matrix(0,8,2)
CuantilesD <- matrix(0,8,2)
colnames(CuantilesA) <- c('LimInf','LimSup')
colnames(CuantilesD) <- c('LimInf','LimSup')
rownames(CuantilesA) <- c('65','70','75','80','85','90','95','99')
rownames(CuantilesD) <- c('65','70','75','80','85','90','95','99')
CuantilesA[1,1] <-CuantilesData[8]; CuantilesA[1,2] <-CuantilesData[9]
CuantilesA[2,1] <-CuantilesData[7]; CuantilesA[2,2] <-CuantilesData[10]
CuantilesA[3,1] <-CuantilesData[6]; CuantilesA[3,2] <-CuantilesData[11]
CuantilesA[4,1] <-CuantilesData[5]; CuantilesA[4,2] <-CuantilesData[12]
CuantilesA[5,1] <-CuantilesData[4]; CuantilesA[5,2] <-CuantilesData[13]
CuantilesA[6,1] <-CuantilesData[3]; CuantilesA[6,2] <-CuantilesData[14]
CuantilesA[7,1] <-CuantilesData[2]; CuantilesA[7,2] <-CuantilesData[15]
CuantilesA[8,1] <-CuantilesData[1]; CuantilesA[8,2] <-CuantilesData[16]
CuantilesD[1,1] <-Cuantilillos[8];  CuantilesD[1,2] <-Cuantilillos[9]
CuantilesD[2,1] <-Cuantilillos[7];  CuantilesD[2,2] <-Cuantilillos[10]
CuantilesD[3,1] <-Cuantilillos[6];  CuantilesD[3,2] <-Cuantilillos[11]
CuantilesD[4,1] <-Cuantilillos[5];  CuantilesD[4,2] <-Cuantilillos[12]
CuantilesD[5,1] <-Cuantilillos[4];  CuantilesD[5,2] <-Cuantilillos[13]
CuantilesD[6,1] <-Cuantilillos[3];  CuantilesD[6,2] <-Cuantilillos[14]
CuantilesD[7,1] <-Cuantilillos[2];  CuantilesD[7,2] <-Cuantilillos[15]
CuantilesD[8,1] <-Cuantilillos[1];  CuantilesD[8,2] <-Cuantilillos[16]

print(CuantilesD)
```

```{r}
print(CuantilesA)
```

```{r}
col_sequence <- rainbow(n = 7, alpha = 0.35, start = 0, end = 1)
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2 pEhEx - DATA (sample 2)', lty = 9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[2,1], lty=2, col="darkblue"); # 70% INFERIOR
abline(v=CuantilesA[2,2], lty=2, col="darkblue") # 70% SUPERIOR
abline(v=CuantilesA[3,1], lty=2, col="aquamarine4"); # 75% INFERIOR
abline(v=CuantilesA[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesA[5,1], lty=2, col="brown"); # 85% INFERIOR
abline(v=CuantilesA[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesA[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesA[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesA[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesA[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesA[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesA[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2   pEhEx - ADJUSTED (sample 2)', lty=9)

abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[2,1], lty=2, col="darkblue");  # 70% INFERIOR
abline(v=CuantilesD[2,2], lty=2, col="darkblue"); # 70% SUPERIOR
abline(v=CuantilesD[3,1], lty=2, col="aquamarine4");  # 75% INFERIOR
abline(v=CuantilesD[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesD[5,1], lty=2, col="brown");  # 85% INFERIOR
abline(v=CuantilesD[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesD[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesD[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesD[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesD[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesD[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesD[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
```


### Grafica Cuantiles del $65\%$ y $80\%$


```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2  pEhEx - DATA (sample 2)', lty=9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2  BaseMean - ADJUSTED (sample 2)', lty=9)

abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
```


### Grafica Cuantiles del $70\%$ y $85\%$


```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence, 
     main = 'Normalized Log2 pEhEx - DATA (sample 2)', lty=9)

abline(v=CuantilesA[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesA[2,2], lty=2, col="darkblue")
abline(v=CuantilesA[5,1], lty=2, col="brown"); 
abline(v=CuantilesA[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2  pEhEx - ADJUSTED (sample 2)', lty=9)

abline(v=CuantilesD[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesD[2,2], lty=2, col="darkblue")
abline(v=CuantilesD[5,1], lty=2, col="brown"); 
abline(v=CuantilesD[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))
```

## Muestra 3

```{r}
log2sample3 <- data5$log2sample3; head(mean(log2sample3)); head(sd(log2sample3))
```

```{r}
head(log2sample3,5)
```

```{r}
ndata5    <- length(log2sample3)
hist(log2sample3, breaks = nbreaks, col= rainbow(25,0.3), 
     main = 'Log2 sample2')
```

```{r}
meanlog2sample3 <- mean(log2sample3); head(meanlog2sample3)
```

```{r}
StdDevlog2sample3 <- sd(log2sample3); head(StdDevlog2sample3)
```

```{r}
Normlog2sample3 <- (log2sample3-meanlog2sample3)/StdDevlog2sample3; head(Normlog2sample3)
tst<- Normlog2sample3
```

```{r}
hist(tst, breaks = nbreaks, col= 1:5, 
     main = 'Normalized Log2sample1',
     xlab='pEhEx1',
     ylab= 'Frequency pEhEx')
```

**Ajustando Modelos**

```{r}
fw1<-fitdist(tst, "norm")
plotdist(tst, histo = TRUE, demp = TRUE)
```

```{r}
nnorm.f <- fitdist(tst,"norm")
summary(nnorm.f)
```

```{r}
par(mfrow=c(2,2))
denscomp(nnorm.f,legendtext = 'Dist Normal')
qqcomp(nnorm.f,legendtext = 'Dist Normal')
cdfcomp(nnorm.f,legendtext = 'Dist Normal')
ppcomp(nnorm.f,legendtext = 'Dist Normal')
```

```{r}
probs <- c();
probs[8] = 0.175;  probs[9] = 0.825; 
probs[7] = 0.15;   probs[10] = 0.85;   
probs[6] = 0.125;  probs[11] = 0.875; 
probs[5] = 0.1;    probs[12] = 0.9;    
probs[4] = 0.075;  probs[13] = 0.925; 
probs[3] = 0.05;   probs[14] = 0.95;   
probs[2] = 0.025;  probs[15] = 0.975; 
probs[1] = 0.005;  probs[16] = 0.995;  
CuantilesData <- quantile(tst,prob = probs)
CuantilesModel <- qnorm(probs, mean=0, sd=1)
Cuantilillos <- t(CuantilesModel)
colnames(Cuantilillos) <- c('0.5%','2.5%','5%','7.5%',
                            '10%','12.5%','15%','17.5%',
                            '82.5%','85%','87.5%','90%',
                            '92.5%','95%','97.5%','99.5%')
Cuantilillos <- t(Cuantilillos)
colnames(Cuantilillos) <- c('Cuantiles Ajuste')
print(Cuantilillos)
```

```{r}
CuantilesA <- matrix(0,8,2)
CuantilesD <- matrix(0,8,2)
colnames(CuantilesA) <- c('LimInf','LimSup')
colnames(CuantilesD) <- c('LimInf','LimSup')
rownames(CuantilesA) <- c('65','70','75','80','85','90','95','99')
rownames(CuantilesD) <- c('65','70','75','80','85','90','95','99')
CuantilesA[1,1] <-CuantilesData[8]; CuantilesA[1,2] <-CuantilesData[9]
CuantilesA[2,1] <-CuantilesData[7]; CuantilesA[2,2] <-CuantilesData[10]
CuantilesA[3,1] <-CuantilesData[6]; CuantilesA[3,2] <-CuantilesData[11]
CuantilesA[4,1] <-CuantilesData[5]; CuantilesA[4,2] <-CuantilesData[12]
CuantilesA[5,1] <-CuantilesData[4]; CuantilesA[5,2] <-CuantilesData[13]
CuantilesA[6,1] <-CuantilesData[3]; CuantilesA[6,2] <-CuantilesData[14]
CuantilesA[7,1] <-CuantilesData[2]; CuantilesA[7,2] <-CuantilesData[15]
CuantilesA[8,1] <-CuantilesData[1]; CuantilesA[8,2] <-CuantilesData[16]
CuantilesD[1,1] <-Cuantilillos[8];  CuantilesD[1,2] <-Cuantilillos[9]
CuantilesD[2,1] <-Cuantilillos[7];  CuantilesD[2,2] <-Cuantilillos[10]
CuantilesD[3,1] <-Cuantilillos[6];  CuantilesD[3,2] <-Cuantilillos[11]
CuantilesD[4,1] <-Cuantilillos[5];  CuantilesD[4,2] <-Cuantilillos[12]
CuantilesD[5,1] <-Cuantilillos[4];  CuantilesD[5,2] <-Cuantilillos[13]
CuantilesD[6,1] <-Cuantilillos[3];  CuantilesD[6,2] <-Cuantilillos[14]
CuantilesD[7,1] <-Cuantilillos[2];  CuantilesD[7,2] <-Cuantilillos[15]
CuantilesD[8,1] <-Cuantilillos[1];  CuantilesD[8,2] <-Cuantilillos[16]
print(CuantilesD)
```

```{r}
print(CuantilesA)
```

**Creación de histogramas**

```{r}
col_sequence <- rainbow(n = 7, alpha = 0.35, start = 0, end = 1)
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2 pEhEx - DATA (sample 3)', lty = 9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[2,1], lty=2, col="darkblue"); # 70% INFERIOR
abline(v=CuantilesA[2,2], lty=2, col="darkblue") # 70% SUPERIOR
abline(v=CuantilesA[3,1], lty=2, col="aquamarine4"); # 75% INFERIOR
abline(v=CuantilesA[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesA[5,1], lty=2, col="brown"); # 85% INFERIOR
abline(v=CuantilesA[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesA[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesA[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesA[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesA[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesA[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesA[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2   pEhEx - ADJUSTED (sample 3)', lty=9)

abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[2,1], lty=2, col="darkblue");  # 70% INFERIOR
abline(v=CuantilesD[2,2], lty=2, col="darkblue"); # 70% SUPERIOR
abline(v=CuantilesD[3,1], lty=2, col="aquamarine4");  # 75% INFERIOR
abline(v=CuantilesD[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesD[5,1], lty=2, col="brown");  # 85% INFERIOR
abline(v=CuantilesD[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesD[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesD[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesD[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesD[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesD[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesD[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
```


### Grafica Cuantiles del $65\%$ y $80\%$

```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2  pEhEx - DATA (sample 2)', lty=9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2  BaseMean - ADJUSTED (sample 3)', lty=9)

abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
```


### Grafica Cuantiles del $70\%$ y $85\%$

```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence, 
     main = 'Normalized Log2 pEhEx - DATA (sample 3)', lty=9)

abline(v=CuantilesA[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesA[2,2], lty=2, col="darkblue")
abline(v=CuantilesA[5,1], lty=2, col="brown"); 
abline(v=CuantilesA[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2  pEhEx - ADJUSTED (sample 3)', lty=9)

abline(v=CuantilesD[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesD[2,2], lty=2, col="darkblue")
abline(v=CuantilesD[5,1], lty=2, col="brown"); 
abline(v=CuantilesD[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))

```

## Muestra pEhExvsumasM1

```{r}
log2vsumasM1 <- data5$log2samplevsumasM1; head(mean(log2vsumasM1)); head(sd(log2vsumasM1))
```


```{r}
head(log2vsumasM1,5)
```

```{r}
ndata5    <- length(log2vsumasM1)
hist(log2vsumasM1, breaks = nbreaks, col= rainbow(25,0.3), 
     main = 'Log2vsumasM1')
```

```{r}
meanlog2vsumasM1 <- mean(log2vsumasM1); head(meanlog2vsumasM1)
StdDevlog2vsumasM1 <- sd(log2vsumasM1); head(StdDevlog2vsumasM1)
```

```{r}
Normlog2vsumasM1 <- (log2vsumasM1-meanlog2vsumasM1)/StdDevlog2vsumasM1; head(Normlog2vsumasM1)
tst<- Normlog2vsumasM1
```

**Primer histograma**

```{r}
hist(tst, breaks = nbreaks, col= 1:5, 
     main = 'Normalized Log2vsumasM1',
     xlab='pEhEx1',
     ylab= 'Frequency pEhEx')
```

**Ajustando modelo**

```{r}
fw1<-fitdist(tst, "norm")
plotdist(tst, histo = TRUE, demp = TRUE)
```

```{r}
nnorm.f <- fitdist(tst,"norm")
summary(nnorm.f)
```

```{r}
par(mfrow=c(2,2))
denscomp(nnorm.f,legendtext = 'Dist Normal')
qqcomp(nnorm.f,legendtext = 'Dist Normal')
cdfcomp(nnorm.f,legendtext = 'Dist Normal')
ppcomp(nnorm.f,legendtext = 'Dist Normal')
```

```{r}
probs <- c();
probs[8] = 0.175;  probs[9] = 0.825; 
probs[7] = 0.15;   probs[10] = 0.85;   
probs[6] = 0.125;  probs[11] = 0.875; 
probs[5] = 0.1;    probs[12] = 0.9;    
probs[4] = 0.075;  probs[13] = 0.925; 
probs[3] = 0.05;   probs[14] = 0.95;   
probs[2] = 0.025;  probs[15] = 0.975; 
probs[1] = 0.005;  probs[16] = 0.995;  
CuantilesData <- quantile(tst,prob = probs)
CuantilesModel <- qnorm(probs, mean=0, sd=1)
Cuantilillos <- t(CuantilesModel)
colnames(Cuantilillos) <- c('0.5%','2.5%','5%','7.5%',
                            '10%','12.5%','15%','17.5%',
                            '82.5%','85%','87.5%','90%',
                            '92.5%','95%','97.5%','99.5%')
Cuantilillos <- t(Cuantilillos)
colnames(Cuantilillos) <- c('Cuantiles Ajuste')
print(Cuantilillos)
```

```{r}
CuantilesA <- matrix(0,8,2)
CuantilesD <- matrix(0,8,2)
colnames(CuantilesA) <- c('LimInf','LimSup')
colnames(CuantilesD) <- c('LimInf','LimSup')
rownames(CuantilesA) <- c('65','70','75','80','85','90','95','99')
rownames(CuantilesD) <- c('65','70','75','80','85','90','95','99')
CuantilesA[1,1] <-CuantilesData[8]; CuantilesA[1,2] <-CuantilesData[9]
CuantilesA[2,1] <-CuantilesData[7]; CuantilesA[2,2] <-CuantilesData[10]
CuantilesA[3,1] <-CuantilesData[6]; CuantilesA[3,2] <-CuantilesData[11]
CuantilesA[4,1] <-CuantilesData[5]; CuantilesA[4,2] <-CuantilesData[12]
CuantilesA[5,1] <-CuantilesData[4]; CuantilesA[5,2] <-CuantilesData[13]
CuantilesA[6,1] <-CuantilesData[3]; CuantilesA[6,2] <-CuantilesData[14]
CuantilesA[7,1] <-CuantilesData[2]; CuantilesA[7,2] <-CuantilesData[15]
CuantilesA[8,1] <-CuantilesData[1]; CuantilesA[8,2] <-CuantilesData[16]
CuantilesD[1,1] <-Cuantilillos[8];  CuantilesD[1,2] <-Cuantilillos[9]
CuantilesD[2,1] <-Cuantilillos[7];  CuantilesD[2,2] <-Cuantilillos[10]
CuantilesD[3,1] <-Cuantilillos[6];  CuantilesD[3,2] <-Cuantilillos[11]
CuantilesD[4,1] <-Cuantilillos[5];  CuantilesD[4,2] <-Cuantilillos[12]
CuantilesD[5,1] <-Cuantilillos[4];  CuantilesD[5,2] <-Cuantilillos[13]
CuantilesD[6,1] <-Cuantilillos[3];  CuantilesD[6,2] <-Cuantilillos[14]
CuantilesD[7,1] <-Cuantilillos[2];  CuantilesD[7,2] <-Cuantilillos[15]
CuantilesD[8,1] <-Cuantilillos[1];  CuantilesD[8,2] <-Cuantilillos[16]
print(CuantilesD)
```

```{r}
print(CuantilesA)
```

**Histogramas**

```{r}
col_sequence <- rainbow(n = 7, alpha = 0.35, start = 0, end = 1)
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM1 pEhEx - DATA', lty = 9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[2,1], lty=2, col="darkblue"); # 70% INFERIOR
abline(v=CuantilesA[2,2], lty=2, col="darkblue") # 70% SUPERIOR
abline(v=CuantilesA[3,1], lty=2, col="aquamarine4"); # 75% INFERIOR
abline(v=CuantilesA[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesA[5,1], lty=2, col="brown"); # 85% INFERIOR
abline(v=CuantilesA[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesA[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesA[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesA[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesA[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesA[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesA[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM1   pEhEx - ADJUSTED', lty=9)

abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[2,1], lty=2, col="darkblue");  # 70% INFERIOR
abline(v=CuantilesD[2,2], lty=2, col="darkblue"); # 70% SUPERIOR
abline(v=CuantilesD[3,1], lty=2, col="aquamarine4");  # 75% INFERIOR
abline(v=CuantilesD[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesD[5,1], lty=2, col="brown");  # 85% INFERIOR
abline(v=CuantilesD[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesD[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesD[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesD[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesD[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesD[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesD[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
```


### Grafica Cuantiles del $65\%$ y $80\%$

```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM1  pEhEx - DATA', lty=9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM1  - ADJUSTED', lty=9)

abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
```


### Grafica Cuantiles del $70\%$ y $85\%$

```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence, 
     main = 'Normalized Log2vsumasM1 pEhEx - DATA', lty=9)

abline(v=CuantilesA[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesA[2,2], lty=2, col="darkblue")
abline(v=CuantilesA[5,1], lty=2, col="brown"); 
abline(v=CuantilesA[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM1  pEhEx - ADJUSTED', lty=9)

abline(v=CuantilesD[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesD[2,2], lty=2, col="darkblue")
abline(v=CuantilesD[5,1], lty=2, col="brown"); 
abline(v=CuantilesD[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))
```


## Muestra pEhExvsumasM2


```{r}
log2vsumasM2 <- data5$log2samplevsumasM2; head(mean(log2vsumasM2)); head(sd(log2vsumasM2))
```

```{r}
head(log2vsumasM2,5)
```

**Primer Histograma**

```{r}
ndata5    <- length(log2vsumasM2)
hist(log2vsumasM2, breaks = nbreaks, col= rainbow(25,0.3), 
     main = 'Log2vsumasM2')
```

```{r}
meanlog2vsumasM2 <- mean(log2vsumasM2); head(meanlog2vsumasM2)
StdDevlog2vsumasM2 <- sd(log2vsumasM2); head(StdDevlog2vsumasM2)
Normlog2vsumasM2 <- (log2vsumasM2-meanlog2vsumasM2)/StdDevlog2vsumasM2; head(Normlog2vsumasM2)
tst<- Normlog2vsumasM2
```

** Segundo Histograma**

```{r}
hist(tst, breaks = nbreaks, col= 1:5, 
     main = 'Normalized Log2vsumasM2',
     xlab='pEhEx1',
     ylab= 'Frequency pEhEx')
```

**Ajustando modelo**

```{r}
fw1<-fitdist(tst, "norm")
plotdist(tst, histo = TRUE, demp = TRUE)
```

```{r}
nnorm.f <- fitdist(tst,"norm")
summary(nnorm.f)
par(mfrow=c(2,2))
denscomp(nnorm.f,legendtext = 'Dist Normal')
qqcomp(nnorm.f,legendtext = 'Dist Normal')
cdfcomp(nnorm.f,legendtext = 'Dist Normal')
ppcomp(nnorm.f,legendtext = 'Dist Normal')
```

**Cálculo de cuantiles**

```{r}
probs <- c();
probs[8] = 0.175;  probs[9] = 0.825; 
probs[7] = 0.15;   probs[10] = 0.85;   
probs[6] = 0.125;  probs[11] = 0.875; 
probs[5] = 0.1;    probs[12] = 0.9;    
probs[4] = 0.075;  probs[13] = 0.925; 
probs[3] = 0.05;   probs[14] = 0.95;   
probs[2] = 0.025;  probs[15] = 0.975; 
probs[1] = 0.005;  probs[16] = 0.995;  
CuantilesData <- quantile(tst,prob = probs)
CuantilesModel <- qnorm(probs, mean=0, sd=1)
Cuantilillos <- t(CuantilesModel)
colnames(Cuantilillos) <- c('0.5%','2.5%','5%','7.5%',
                            '10%','12.5%','15%','17.5%',
                            '82.5%','85%','87.5%','90%',
                            '92.5%','95%','97.5%','99.5%')
Cuantilillos <- t(Cuantilillos)
colnames(Cuantilillos) <- c('Cuantiles Ajuste')
print(Cuantilillos)
```

```{r}
CuantilesA <- matrix(0,8,2)
CuantilesD <- matrix(0,8,2)
colnames(CuantilesA) <- c('LimInf','LimSup')
colnames(CuantilesD) <- c('LimInf','LimSup')
rownames(CuantilesA) <- c('65','70','75','80','85','90','95','99')
rownames(CuantilesD) <- c('65','70','75','80','85','90','95','99')
CuantilesA[1,1] <-CuantilesData[8]; CuantilesA[1,2] <-CuantilesData[9]
CuantilesA[2,1] <-CuantilesData[7]; CuantilesA[2,2] <-CuantilesData[10]
CuantilesA[3,1] <-CuantilesData[6]; CuantilesA[3,2] <-CuantilesData[11]
CuantilesA[4,1] <-CuantilesData[5]; CuantilesA[4,2] <-CuantilesData[12]
CuantilesA[5,1] <-CuantilesData[4]; CuantilesA[5,2] <-CuantilesData[13]
CuantilesA[6,1] <-CuantilesData[3]; CuantilesA[6,2] <-CuantilesData[14]
CuantilesA[7,1] <-CuantilesData[2]; CuantilesA[7,2] <-CuantilesData[15]
CuantilesA[8,1] <-CuantilesData[1]; CuantilesA[8,2] <-CuantilesData[16]
CuantilesD[1,1] <-Cuantilillos[8];  CuantilesD[1,2] <-Cuantilillos[9]
CuantilesD[2,1] <-Cuantilillos[7];  CuantilesD[2,2] <-Cuantilillos[10]
CuantilesD[3,1] <-Cuantilillos[6];  CuantilesD[3,2] <-Cuantilillos[11]
CuantilesD[4,1] <-Cuantilillos[5];  CuantilesD[4,2] <-Cuantilillos[12]
CuantilesD[5,1] <-Cuantilillos[4];  CuantilesD[5,2] <-Cuantilillos[13]
CuantilesD[6,1] <-Cuantilillos[3];  CuantilesD[6,2] <-Cuantilillos[14]
CuantilesD[7,1] <-Cuantilillos[2];  CuantilesD[7,2] <-Cuantilillos[15]
CuantilesD[8,1] <-Cuantilillos[1];  CuantilesD[8,2] <-Cuantilillos[16]
print(CuantilesD)
```

```{r}
print(CuantilesA)
```

**Histogramas**

```{r}
col_sequence <- rainbow(n = 7, alpha = 0.35, start = 0, end = 1)
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM2 pEhEx - DATA', lty = 9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[2,1], lty=2, col="darkblue"); # 70% INFERIOR
abline(v=CuantilesA[2,2], lty=2, col="darkblue") # 70% SUPERIOR
abline(v=CuantilesA[3,1], lty=2, col="aquamarine4"); # 75% INFERIOR
abline(v=CuantilesA[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesA[5,1], lty=2, col="brown"); # 85% INFERIOR
abline(v=CuantilesA[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesA[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesA[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesA[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesA[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesA[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesA[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM2   pEhEx - ADJUSTED', lty=9)

abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[2,1], lty=2, col="darkblue");  # 70% INFERIOR
abline(v=CuantilesD[2,2], lty=2, col="darkblue"); # 70% SUPERIOR
abline(v=CuantilesD[3,1], lty=2, col="aquamarine4");  # 75% INFERIOR
abline(v=CuantilesD[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesD[5,1], lty=2, col="brown");  # 85% INFERIOR
abline(v=CuantilesD[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesD[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesD[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesD[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesD[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesD[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesD[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
```

### Grafica Cuantiles del $65\%$ y $80\%$

```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM2  pEhEx - DATA', lty=9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM2  - ADJUSTED', lty=9)

abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
```

### Grafica Cuantiles del $70\%$ y $85\%$

```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence, 
     main = 'Normalized Log2vsumasM2 pEhEx - DATA', lty=9)

abline(v=CuantilesA[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesA[2,2], lty=2, col="darkblue")
abline(v=CuantilesA[5,1], lty=2, col="brown"); 
abline(v=CuantilesA[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM2  pEhEx - ADJUSTED', lty=9)

abline(v=CuantilesD[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesD[2,2], lty=2, col="darkblue")
abline(v=CuantilesD[5,1], lty=2, col="brown"); 
abline(v=CuantilesD[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))
```

## Muestra pEhExvsumasM3

```{r}
log2vsumasM3 <- data5$log2samplevsumasM3; head(mean(log2vsumasM3)); head(sd(log2vsumasM3))
```

```{r}
head(log2vsumasM3,5)
```

```{r}
ndata5    <- length(log2vsumasM3)
```

** Primer histograma**

```{r}
hist(log2vsumasM3, breaks = nbreaks, col= rainbow(25,0.3), 
     main = 'Log2vsumasM3')
```

```{r}
meanlog2vsumasM3 <- mean(log2vsumasM3); head(meanlog2vsumasM3)
StdDevlog2vsumasM3 <- sd(log2vsumasM3); head(StdDevlog2vsumasM3)
Normlog2vsumasM3 <- (log2vsumasM3-meanlog2vsumasM3)/StdDevlog2vsumasM3; head(Normlog2vsumasM3)
tst<- Normlog2vsumasM3
```

**Segundo histograma**

```{r}
hist(tst, breaks = nbreaks, col= 1:5, 
     main = 'Normalized Log2vsumasM3',
     xlab='pEhEx1',
     ylab= 'Frequency pEhEx')
```

**Ajustando modelo**

```{r}
fw1<-fitdist(tst, "norm")
plotdist(tst, histo = TRUE, demp = TRUE)
```

```{r}
nnorm.f <- fitdist(tst,"norm")
summary(nnorm.f)
par(mfrow=c(2,2))
denscomp(nnorm.f,legendtext = 'Dist Normal')
qqcomp(nnorm.f,legendtext = 'Dist Normal')
cdfcomp(nnorm.f,legendtext = 'Dist Normal')
ppcomp(nnorm.f,legendtext = 'Dist Normal')
```

**Calculo de cuantiles**

```{r}
probs <- c();
probs[8] = 0.175;  probs[9] = 0.825; 
probs[7] = 0.15;   probs[10] = 0.85;   
probs[6] = 0.125;  probs[11] = 0.875; 
probs[5] = 0.1;    probs[12] = 0.9;    
probs[4] = 0.075;  probs[13] = 0.925; 
probs[3] = 0.05;   probs[14] = 0.95;   
probs[2] = 0.025;  probs[15] = 0.975; 
probs[1] = 0.005;  probs[16] = 0.995;  
CuantilesData <- quantile(tst,prob = probs)
CuantilesModel <- qnorm(probs, mean=0, sd=1)
Cuantilillos <- t(CuantilesModel)
colnames(Cuantilillos) <- c('0.5%','2.5%','5%','7.5%',
                            '10%','12.5%','15%','17.5%',
                            '82.5%','85%','87.5%','90%',
                            '92.5%','95%','97.5%','99.5%')
Cuantilillos <- t(Cuantilillos)
colnames(Cuantilillos) <- c('Cuantiles Ajuste')
print(Cuantilillos)
```

```{r}
CuantilesA <- matrix(0,8,2)
CuantilesD <- matrix(0,8,2)
colnames(CuantilesA) <- c('LimInf','LimSup')
colnames(CuantilesD) <- c('LimInf','LimSup')
rownames(CuantilesA) <- c('65','70','75','80','85','90','95','99')
rownames(CuantilesD) <- c('65','70','75','80','85','90','95','99')
CuantilesA[1,1] <-CuantilesData[8]; CuantilesA[1,2] <-CuantilesData[9]
CuantilesA[2,1] <-CuantilesData[7]; CuantilesA[2,2] <-CuantilesData[10]
CuantilesA[3,1] <-CuantilesData[6]; CuantilesA[3,2] <-CuantilesData[11]
CuantilesA[4,1] <-CuantilesData[5]; CuantilesA[4,2] <-CuantilesData[12]
CuantilesA[5,1] <-CuantilesData[4]; CuantilesA[5,2] <-CuantilesData[13]
CuantilesA[6,1] <-CuantilesData[3]; CuantilesA[6,2] <-CuantilesData[14]
CuantilesA[7,1] <-CuantilesData[2]; CuantilesA[7,2] <-CuantilesData[15]
CuantilesA[8,1] <-CuantilesData[1]; CuantilesA[8,2] <-CuantilesData[16]
CuantilesD[1,1] <-Cuantilillos[8];  CuantilesD[1,2] <-Cuantilillos[9]
CuantilesD[2,1] <-Cuantilillos[7];  CuantilesD[2,2] <-Cuantilillos[10]
CuantilesD[3,1] <-Cuantilillos[6];  CuantilesD[3,2] <-Cuantilillos[11]
CuantilesD[4,1] <-Cuantilillos[5];  CuantilesD[4,2] <-Cuantilillos[12]
CuantilesD[5,1] <-Cuantilillos[4];  CuantilesD[5,2] <-Cuantilillos[13]
CuantilesD[6,1] <-Cuantilillos[3];  CuantilesD[6,2] <-Cuantilillos[14]
CuantilesD[7,1] <-Cuantilillos[2];  CuantilesD[7,2] <-Cuantilillos[15]
CuantilesD[8,1] <-Cuantilillos[1];  CuantilesD[8,2] <-Cuantilillos[16]
print(CuantilesD)
```

```{r}
print(CuantilesA)
```

**Histogramas**

```{r}
col_sequence <- rainbow(n = 7, alpha = 0.35, start = 0, end = 1)
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM3 pEhEx - DATA', lty = 9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[2,1], lty=2, col="darkblue"); # 70% INFERIOR
abline(v=CuantilesA[2,2], lty=2, col="darkblue") # 70% SUPERIOR
abline(v=CuantilesA[3,1], lty=2, col="aquamarine4"); # 75% INFERIOR
abline(v=CuantilesA[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesA[5,1], lty=2, col="brown"); # 85% INFERIOR
abline(v=CuantilesA[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesA[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesA[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesA[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesA[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesA[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesA[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM3   pEhEx - ADJUSTED', lty=9)

abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[2,1], lty=2, col="darkblue");  # 70% INFERIOR
abline(v=CuantilesD[2,2], lty=2, col="darkblue"); # 70% SUPERIOR
abline(v=CuantilesD[3,1], lty=2, col="aquamarine4");  # 75% INFERIOR
abline(v=CuantilesD[3,2], lty=2, col="aquamarine4"); # 75% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
abline(v=CuantilesD[5,1], lty=2, col="brown");  # 85% INFERIOR
abline(v=CuantilesD[5,2], lty=2, col="brown"); # 85% SUPERIOR
abline(v=CuantilesD[6,1], lty=2, col="red");  # 90% INFERIOR
abline(v=CuantilesD[6,2], lty=2, col="red"); # 90% SUPERIOR
abline(v=CuantilesD[7,1], lty=2, col="blue");  # 95% INFERIOR
abline(v=CuantilesD[7,2], lty=2, col="blue"); # 95% SUPERIOR
abline(v=CuantilesD[8,1], lty=2, col="orange");  # 99% INFERIOR
abline(v=CuantilesD[8,2], lty=2, col="orange"); # 99% SUPERIOR
legend("topright",
       legend=c("65%","70%","75%","80%","85%","90%","95%","99%"), 
       pch=c(1,2,3,4,5,6,7,8),
       col=c("darkgoldenrod4","darkblue","aquamarine4",
             "green", "brown","red","blue","orange"))
```


### Grafica Cuantiles del $65\%$ y $80\%$


```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM3  pEhEx - DATA', lty=9)

abline(v=CuantilesA[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesA[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesA[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesA[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM1  - ADJUSTED', lty=9)

abline(v=CuantilesD[1,1], lty=2, col="darkgoldenrod4"); # 65% INFERIOR
abline(v=CuantilesD[1,2], lty=2, col="darkgoldenrod4"); # 65% SUPERIOR
abline(v=CuantilesD[4,1], lty=2, col="green");  # 80% INFERIOR
abline(v=CuantilesD[4,2], lty=2, col="green"); # 80% SUPERIOR
legend("topright",legend=c("65%","80%"), 
       pch=c(1,2),col=c("darkgoldenrod4","green"))
```


### Grafica Cuantiles del $70\%$ y $85\%$


```{r}
par(mfrow=c(2,1))
hist(tst, breaks = nbreaks, col = col_sequence, 
     main = 'Normalized Log2vsumasM3 pEhEx - DATA', lty=9)

abline(v=CuantilesA[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesA[2,2], lty=2, col="darkblue")
abline(v=CuantilesA[5,1], lty=2, col="brown"); 
abline(v=CuantilesA[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))
hist(tst, breaks = nbreaks, col = col_sequence,
     main = 'Normalized Log2vsumasM3  pEhEx - ADJUSTED', lty=9)

abline(v=CuantilesD[2,1], lty=2, col="darkblue"); 
abline(v=CuantilesD[2,2], lty=2, col="darkblue")
abline(v=CuantilesD[5,1], lty=2, col="brown"); 
abline(v=CuantilesD[5,2], lty=2, col="brown")
legend("topright",legend=c("70%","85%"),
       pch=c(1,2),#3,4,5,6,7,8),
       col=c("brown"))
```

